Turbulence in compact to giant HII regions

### 2022-01-08 strucfunc_paper.tex
Move velocity fields section

\subsection{Spectroscopic datasets}

%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
\newcommand\xx{\ensuremath{\boldsymbol{x}}}
Wherever possible, we calculate the centroid velocity \(V_c\)
directly as the normalized first velocity moment of the spectral line intensity profile
for each plane-of-sky position \(\xx\) on the nebula:
\(V_{c}(\xx) = M_1(\xx) / M_0(\xx)\).
The \(k\)th unnormalized moment \(M_k\) of the continuum-subtracted
spectral intensity profile \(I(v)\)
is defined as
\begin{equation}
  \label{eq:kth-moment}
  M_k = \int_{\Delta v} I(v) \, v^k \, dv
\end{equation}
where the Doppler velocity \(v\) is calculated according to
the \texttt{VOPT} convention
\citetext{Eq.~[32] of \citealt{Greisen:2006a}}:
\begin{equation}
  \label{eq:optical-velocity}
  v \equiv c\, (\lambda - \lambda_0) / \lambda_0 ,
\end{equation}
where \(\lambda\) is the observed wavelength,
\(\lambda_0\) is the rest wavelength, and \(c\) is the speed of light.
The spectral window \(\Delta v\) is chosen to be just large enough to include
the entire \ha{} emission line.
So long as the signal-to-noise is high enough,
this mean velocity can be calculated to a much higher precision
than the nominal velocity resolution of the spectrograph. 
In a few cases, as noted below, we are working with already reduced data,
which are provided in the form of Gaussian fits to the line profiles.
In the cases where multiple Gaussian components have been fitted,
we take the flux-weighted mean velocity of these components to be the centroid.

The observed RMS spectral line width \(\sigma'\) can likewise be found from
the second velocity moment as
\begin{equation}
  \label{eq:observed-sigma}
  \sigma'(\xx)^2  = [M_2(\xx) / M_0(\xx)] - V_{c}(\xx)^2 .
\end{equation}
However, many different broadening mechanisms contribute to this width,
including the finite spectral resolution \(\sigma_{\mathrm{ins}}\),
fine-structure splitting \(\sigma_{\mathrm{fs}}\),
and thermal Doppler broadening \(\sigma_{\mathrm{t}}\).
In the approximation that all these broadening mechanisms are independent
and described by Gaussian profiles, then the dispersion of
line-of-sight velocities due to bulk motions \(\sigma\los\) can be found
by subtracting these contributions in quadrature from the observed width:
\begin{equation}
  \label{eq:sigma-los}
  \sigma\los^2 = \sigma'^2 - \sigma_{\mathrm{ins}}^2 - \sigma_{\mathrm{fs}}^2 - \sigma_{\mathrm{t}}^2 .
\end{equation}

@@

@@

\subsection{Velocity fields of the HII regions}

\textit{Javier 2021-12-28: I'm not quite sure the correct section for this. Since they aren't results, per se, and until now I haven't develop to much discussion with them, I move it here so it end up like Methods and Data, before reporting our findings. }

The Figure \ref{fig:velocity-maps} shows the velocity maps of each HII region in the \halpha\ emission line.
All velocities are relative to the systemic velocity of each region, with more negative velocities shown in blue and more positive velocities in red. The range of velocities is different for each region and is shown in each map. The more negative velocities are shown in blue and more positive velocities are shown in red.
The Figure \ref{fig:hist} shows the probability density functions of our sample of HII regions.
All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.

>>>>

\subsection{Spectroscopic datasets}
\label{sec:spectr-datas}
%We use data from \citet{1987A&A...176..347H} and \citet{arthur2016turbulence} to study of turbulence in the Orion Nebula.
%\cite{1987A&A...176..347H} observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
%A Fabry-Pérot interferometer was used with a étalon a separation of 0.5 mm. 
%Interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula. 
%The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.
\newcommand\xx{\ensuremath{\boldsymbol{x}}}
Wherever possible, we calculate the centroid velocity \(V_c\)
directly as the normalized first velocity moment of the spectral line intensity profile
for each plane-of-sky position \(\xx\) on the nebula:
\(V_{c}(\xx) = M_1(\xx) / M_0(\xx)\).
The \(k\)th unnormalized moment \(M_k\) of the continuum-subtracted
spectral intensity profile \(I(v)\)
is defined as
\begin{equation}
  \label{eq:kth-moment}
  M_k = \int_{\Delta v} I(v) \, v^k \, dv
\end{equation}
where the Doppler velocity \(v\) is calculated according to
the \texttt{VOPT} convention
\citetext{Eq.~[32] of \citealt{Greisen:2006a}}:
\begin{equation}
  \label{eq:optical-velocity}
  v \equiv c\, (\lambda - \lambda_0) / \lambda_0 ,
\end{equation}
where \(\lambda\) is the observed wavelength,
\(\lambda_0\) is the rest wavelength, and \(c\) is the speed of light.
The spectral window \(\Delta v\) is chosen to be just large enough to include
the entire \ha{} emission line.
So long as the signal-to-noise is high enough,
this mean velocity can be calculated to a much higher precision
than the nominal velocity resolution of the spectrograph. 
In a few cases, as noted below, we are working with already reduced data,
which are provided in the form of Gaussian fits to the line profiles.
In the cases where multiple Gaussian components have been fitted,
we take the flux-weighted mean velocity of these components to be the centroid.

The observed RMS spectral line width \(\sigma'\) can likewise be found from
the second velocity moment as
\begin{equation}
  \label{eq:observed-sigma}
  \sigma'(\xx)^2  = [M_2(\xx) / M_0(\xx)] - V_{c}(\xx)^2 .
\end{equation}
However, many different broadening mechanisms contribute to this width,
including the finite spectral resolution \(\sigma_{\mathrm{ins}}\),
fine-structure splitting \(\sigma_{\mathrm{fs}}\),
and thermal Doppler broadening \(\sigma_{\mathrm{t}}\).
In the approximation that all these broadening mechanisms are independent
and described by Gaussian profiles, then the dispersion of
line-of-sight velocities due to bulk motions \(\sigma\los\) can be found
by subtracting these contributions in quadrature from the observed width:
\begin{equation}
  \label{eq:sigma-los}
  \sigma\los^2 = \sigma'^2 - \sigma_{\mathrm{ins}}^2 - \sigma_{\mathrm{fs}}^2 - \sigma_{\mathrm{t}}^2 .
\end{equation}
See sec~5.1 of \citet{Garcia-Diaz:2008a} for further details.

@@

% \subsection{Velocity fields of the HII regions}

% \textit{Javier 2021-12-28: I'm not quite sure the correct section for this. Since they aren't results, per se, and until now I haven't develop to much discussion with them, I move it here so it end up like Methods and Data, before reporting our findings. }

Figure~\ref{fig:velocity-maps} shows maps of the \ha{} centroid velocity
\(V_c\) for each \hii{} region in our sample,
calculated as described above in section~\ref{sec:spectr-datas}
and after subtracting the mean systemic velocity in each case.
The color scheme ranges from the most negative velocities in blue
to the most positive velocities in red,
but the amplitude of the velocity fluctuations differs considerably between regions,
as indicated by the color scale bar on each map,
ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
This can be appreciated quantitatively in Figure~\ref{fig:hist},
which shows the probability density function (PDF) of \(V_c\) for each region
on a common velocity scale and arranged in order of decreasing amplitude
of velocity fluctuations. 
All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.

@@
